\documentclass[letterpaper,11pt]{article}
\usepackage{helvet}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{ifthen}
\usepackage{setspace}
\linespread{0.9}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage[colorlinks=true, urlcolor=primaryColor]{hyperref}
\usepackage{fancyhdr}
\usepackage[margin=0.5in, includefoot]{geometry}
\usepackage{fontspec}
\setmainfont{Arial}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{6pt}

% Resume Title Format
\titleformat{\section}{
  \vspace{-8pt}\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Resume Href
\let\hrefWithoutArrow\href
\renewcommand{\href}[2]{
  \hrefWithoutArrow{#1}{
    \ifthenelse{\equal{#2}{}}{ }{#2\ }
    \raisebox{.15ex}{\footnotesize \faExternalLink*}
  }
}

% Resume Item
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{0pt}}
  }
}

% Resume Item No Horizontal Padding
\newcommand{\resumeItemNH}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

% Resume Subheading
\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small#4 \\
    \end{tabular*}\vspace{-6pt}
}

% Resume Project Heading
\newcommand{\resumeProjectHeading}[3]{
  \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \small• #2 & #3 \\
    \end{tabular*}\vspace{0pt}
}

% Resume SubItem
\newcommand{\resumeSubItem}[2]{
  \vspace{-16pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\small#1}: \small#2 \\
  \end{tabular*}\vspace{-4pt}
}

% Resume Project Technologies Item
\newcommand{\resumeProjectTechnologiesItem}[1]{
  \vspace{-16pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\small Technologies}: \small#1 \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt,label={}]}
\renewcommand{\labelitemii}{\raisebox{0.2ex}{\footnotesize \textbullet}}
\newcommand{\resumeSubHeadingListStartBullets}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

% Header
\begin{center}
{\LARGE \textbf{Pin-Chieh(Jay) Hsia}}\\[0.25em]
{Software Engineer}\\[0.1em]
\small Toronto, ON | +1 (416) 564-1450 |
\hrefWithoutArrow{mailto:jayhsia1997@gmail.com}{jayhsia1997@gmail.com} |
\hrefWithoutArrow{https://www.linkedin.com/in/jayhsia1997/}{linkedin.com/in/jayhsia1997} |
\hrefWithoutArrow{https://github.com/jayhsia1997}{github.com/jayhsia1997}
\\[0.4em]
\end{center}

% ---- Summary ----
% \section{Summary}
% Software engineer with over 4 years of specialization in back-end development and proficiency in basic front-end tasks. Recent experience includes role as software application engineer at Trend Micro, focusing on the design and development of back-end architecture. Currently pursuing studies in computer programming in Canada.

% Professional Skills
\section*{Professional Skills}
  \resumeItemListStart
    % Backend
    \resumeItemNH{\textbf{Backend:} Python, FastAPI, Django, RESTful APIs, Cache Systems, Message Queues}
    % Cloud \& DevOps
    \resumeItemNH{\textbf{Cloud \& DevOps:} AWS, Azure, Docker, CI/CD (GitHub Actions), Linux, Firebase}
    % Databases \& Storage
    \resumeItemNH{\textbf{Databases \& Storage:} PostgreSQL, Redis, NoSQL, AWS S3, Firebase Storage}
    % Frontend
    \resumeItemNH{\textbf{Frontend:} JavaScript, TypeScript, React.js, HTML, CSS, Tailwind}
    % Other
    \resumeItemNH{\textbf{Other:} System Design, Unit Test, C++, Git, Scrum, Jira, Design Patterns, Open Telemetry, Cross-team Collaboration}
  \resumeItemListEnd

% Work Experience
\section*{Work Experience}
  \resumeSubHeadingListStart
    % Trend Micro
    \resumeSubheading
      {Software Application Engineer}{Taipei City, Taiwan}
      {Trend Micro}{Sep 2021 -- Feb 2024}
      \resumeItemListStart
        \resumeItemNH{Developed a script for the development team using the pre-commit tool to unify code style and prevent committing sensitive information.}
        \resumeItemNH{Enhanced the Game feature within the Microsoft Teams application through strategic refactoring, optimizing data storage methodologies to nearly double system performance and reduce errors by approximately 90\%.}
        \resumeItemNH{Researched and designed backend architecture for a new internal ticketing system, integrating a Message Queue System to improve workflow flexibility.}
        \resumeItemNH{Created a scheduled task script to store internal company documents as vectors in Azure AI Search, enabling AI chatbot development for knowledge retrieval.}
        \resumeItemNH{Collaborated with HR to design and implement a game-based onboarding application on Microsoft Teams, facilitating efficient knowledge acquisition for new employees.}
      \resumeItemListEnd
    % Taiwan Good Fortune Cloud Co., Ltd.
    \resumeSubheading
      {Python Developer}{Taichung City, Taiwan}
      {Taiwan Good Fortune Cloud Co., Ltd.}{Apr 2020 -- Sep 2021}
      \resumeItemListStart
        \resumeItemNH{Developed and maintained the internal operations and maintenance system, planning, documenting, and building RESTful APIs.}
        \resumeItemNH{Implemented front-end and back-end features, including asynchronous web scraping scripts.}
        \resumeItemNH{Led the restructuring of the system architecture for operations management, reducing server load by over 50\%.}
        \resumeItemNH{Contributed to the implementation of the company's internal ticketing system.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% Education
\section*{Education}
  \resumeSubHeadingListStart
    % Seneca Polytechnic
    \resumeSubheading
      {Seneca Polytechnic}{Toronto, ON}
      {Advanced Diploma in \textbf{Computer Programming \& Analysis}}{Jan 2025 -- Sep 2027}
    % Lunghwa University of Science and Technology
    \resumeSubheading
      {Lunghwa University of Science and Technology}{Taoyuan City, Taiwan}
      {B.S. in \textbf{Electrical Engineering}}{Sep 2015 -- Jun 2019}
  \resumeSubHeadingListEnd

% Projects
\section*{Projects}
  \resumeSubHeadingListStart
    % The Hope Conference App
    \resumeProjectHeading{The Hope Conference App}{Backend Development}{Aug 2024 -- Present}
      \resumeProjectTechnologiesItem{Python, FastAPI, Django, PostgreSQL, Redis, AWS RDS, AWS S3, Docker, CI/CD, Firebase, Render}
      \resumeItemListStart
        \resumeItemNH{Developed a backend system for a Conference APP using FastAPI, integrating Firebase Authentication for user login, and designed APIs for frontend usage.}
        \resumeItemNH{Build a simple Wagtail CMS based on Django to allow administrators to edit the data displayed on the APP.}
      \resumeItemListEnd
    % Personal Website
    \resumeProjectHeading{Personal Website}{Frontend Development}{May 2025 -- Present}
      \resumeProjectTechnologiesItem{React.js, TypeScript, Tailwind, Vite, Firebase}
      \resumeItemListStart
        \resumeItemNH{Developed a personal website using React.js and TypeScript, and deployed it on Firebase Hosting.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\end{document}